---
title: "Comprehension Regressions: First Study"
output:
  html_document: default
  pdf_document: default
---

# Binomial Logistic Regressions — First Study Comprehension

We run binomial logistic regressions to test whether explanation type
(`EXPLN_S1`, `EXPLN_S2`, `EXPLN_S3`) and domain experience predict correct
answers for each comprehension question (Q1–Q10, stored as columns A–J).

Models are fit separately per scenario (Medical Simple, Medical Complex,
IoT Simple, IoT Complex). Benjamini-Hochberg (BH) correction is applied
across the four scenarios **within each predictor term**.

Results include odds ratios (OR), 95% confidence intervals, and
McFadden's R². They are saved to `BH_correction_1stStudy.csv`.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(broom)
library(sjPlot)
library(car)
library(purrr)
```

---

## Load data

```{r load-data}
scores_medicals <- read.csv('./data/firststudy/scores-medicals.csv', header = TRUE)
scores_medicalc <- read.csv('./data/firststudy/scores-medicalc.csv', header = TRUE)
scores_iots     <- read.csv('./data/firststudy/scores-iots.csv',     header = TRUE)
scores_iotc     <- read.csv('./data/firststudy/scores-iotc.csv',     header = TRUE)

prepare_data <- function(df) {
  names(df) <- gsub(" ", "_", names(df))
  df$EXPLN_S1 <- factor(df$EXPLN_S1, levels = c("Unsubstantial", "Hardware", "Trust"))
  df$combined_CS_Experience      <- as.factor(df$combined_CS_Experience)
  df$combined_Medical_Experience <- as.factor(df$combined_Medical_Experience)
  df$combined_IoT_Experience     <- as.factor(df$combined_IoT_Experience)
  df
}

scores_medicals <- prepare_data(scores_medicals)
scores_medicalc <- prepare_data(scores_medicalc)
scores_iots     <- prepare_data(scores_iots)
scores_iotc     <- prepare_data(scores_iotc)
```

---

## Medical Simple

```{r}
regression_results <- scores_medicals
regression_model <- function(dependent_var) {
  formula_str <- as.formula(paste(dependent_var, "~ EXPLN_S1 + EXPLN_S2 + EXPLN_S3 + combined_Medical_Experience + combined_CS_Experience"))
  model <- glm(formula_str, data = regression_results, family = binomial)
  print(summary(model))
  print(Anova(model))
  plot_model(model)
  return(model)
}
scores_medicals = regression_results

```

## MedS 1

```{r}
results <- regression_model("A")
```
## MedS 2

```{r}
results <- regression_model("B")
```

## MedS 3

```{r}
results <- regression_model("C")
```

## MedS 4

```{r}
results <- regression_model("D")
```

## MedS 5

```{r}
results <- regression_model("E")
```

## MedS 6

```{r}
results <- regression_model("F")
```

## MedS 7

```{r}
results <- regression_model("G")
```

## MedS 8

```{r}
results <- regression_model("H")
```

## MedS 9

```{r}
results <- regression_model("I")
```


## MedS 10

```{r}
results <- regression_model("J")
```

## Medical Complex

```{r}
regression_results <- scores_medicalc


regression_model <- function(dependent_var) {
  formula_str <- as.formula(paste(dependent_var, "~ EXPLN_S1 + EXPLN_S2 + EXPLN_S3 + combined_Medical_Experience + combined_CS_Experience"))
  model <- glm(formula_str, data = regression_results, family = binomial)
  print(summary(model))
  print(Anova(model))
  plot_model(model)
  return(model)
}

scores_medicalc = regression_results
```

## MedC 1

```{r}
results <- regression_model("A")
```
## MedC 2

```{r}
results <- regression_model("B")
```

## MedC 3

```{r}
results <- regression_model("C")
```

## MedC 4

```{r}
results <- regression_model("D")
```

## MedC 5

```{r}
results <- regression_model("E")
```

## MedC 6

```{r}
results <- regression_model("F")
```

## MedC 7

```{r}
results <- regression_model("G")
```

## MedC 8

```{r}
results <- regression_model("H")
```

## MedC 9

```{r}
results <- regression_model("I")
```


## MedC 10

```{r}
results <- regression_model("J")
```

## IoT Simple

```{r}
regression_results <- scores_iots

regression_model <- function(dependent_var) {
  formula_str <- as.formula(paste(dependent_var, "~ EXPLN_S1 + EXPLN_S2 + EXPLN_S3 + combined_IoT_Experience + combined_CS_Experience"))
  model <- glm(formula_str, data = regression_results, family = binomial)
  print(summary(model))
  print(Anova(model))
  plot_model(model)
  return(model)
}
scores_iots = regression_results

```

## IoTS 1

```{r}
results <- regression_model("A")
```
## IoTS 2

```{r}
results <- regression_model("B")
```

## IoTS 3

```{r}
results <- regression_model("C")
```

## IoTS 4

```{r}
results <- regression_model("D")
```

## IoTS 5

```{r}
results <- regression_model("E")
```

## IoTS 6

```{r}
results <- regression_model("F")
```

## IoTS 7

```{r}
results <- regression_model("G")
```

## IoTS 8

```{r}
results <- regression_model("H")
```

## IoTS 9

```{r}
results <- regression_model("I")
```


## IoTS 10

```{r}
results <- regression_model("J")
```

Binomial logistic regression to check if demographic and experience
factors affect score (IoT Complex)

```{r}
regression_results <- scores_iotc


regression_model <- function(dependent_var) {
  formula_str <- as.formula(paste(dependent_var, "~ EXPLN_S1 + EXPLN_S2 + EXPLN_S3 + combined_IoT_Experience + combined_CS_Experience"))
  model <- glm(formula_str, data = regression_results, family = binomial)
  print(summary(model))
  print(Anova(model))
  plot_model(model)
  return(model)
}
scores_iotc = regression_results

```

## IoTC 1

```{r}
results <- regression_model("A")
```
## IoTC 2

```{r}
results <- regression_model("B")
```

## IoTC 3

```{r}
results <- regression_model("C")
```

## IoTC 4

```{r}
results <- regression_model("D")
```

## IoTC 5

```{r}
results <- regression_model("E")
```

## IoTC 6

```{r}
results <- regression_model("F")
```

## IoTC 7

```{r}
results <- regression_model("G")
```

## IoTC 8

```{r}
results <- regression_model("H")
```

## IoTC 9

```{r}
results <- regression_model("I")
```


## IoTC 10

```{r}
results <- regression_model("J")
```

# Corrections

```{r}



run_BH_logistics <- function(dependent_var) {
  scenario_data <- list(
    MedicalSimple  = scores_medicals,
    MedicalComplex = scores_medicalc,
    IoTSimple      = scores_iots,
    IoTComplex     = scores_iotc
  )

  get_model_terms <- function(df, scenario) {
    exp_var <- if (grepl("Medical", scenario))
      "combined_Medical_Experience" else "combined_IoT_Experience"
    
    f <- as.formula(paste(
      dependent_var,
      "~ EXPLN_S1 + EXPLN_S2 + EXPLN_S3 +",
      exp_var, "+ combined_CS_Experience"
    ))
    
    model <- glm(f, data = df, family = binomial)
    broom::tidy(model) |> dplyr::mutate(Scenario = scenario)
  }

  res <- purrr::imap_dfr(scenario_data, get_model_terms) |>
    dplyr::filter(term != "(Intercept)") |>
    dplyr::group_by(term) |>
    dplyr::mutate(q_value = p.adjust(p.value, method = "BH")) |>
    dplyr::ungroup() |>
    dplyr::mutate(
      Question = dependent_var,
      PreSig = p.value <= 0.05,
      PostSig = q_value <= 0.05,
      Status = dplyr::case_when(
        PreSig & !PostSig ~ "Lost significance",
        !PreSig & PostSig ~ "Gained significance",
        PreSig & PostSig  ~ "Stayed significant",
        TRUE              ~ ""
      )
    ) |>
    dplyr::select(Question, Scenario, term, p.value, q_value, Status)
    invisible(res)
}



lapply(LETTERS[1:10], run_BH_logistics)

holm_results_letters <- purrr::map_dfr(LETTERS[1:10], run_BH_logistics)
write.csv(holm_results_letters, "BH_correction_1stStudy.csv", row.names = FALSE)

```



```{r}

run_Holm_logistics <- function(dependent_var) {
  scenario_data <- list(
    MedicalSimple  = scores_medicals,
    MedicalComplex = scores_medicalc,
    IoTSimple      = scores_iots,
    IoTComplex     = scores_iotc
  )

  get_model_terms <- function(df, scenario) {
    exp_var <- if (grepl("Medical", scenario))
      "combined_Medical_Experience" else "combined_IoT_Experience"
    
    f <- as.formula(paste(
      dependent_var,
      "~ EXPLN_S1 + EXPLN_S2 + EXPLN_S3 +",
      exp_var, "+ combined_CS_Experience"
    ))
    
    model <- glm(f, data = df, family = binomial)
    broom::tidy(model) |> dplyr::mutate(Scenario = scenario)
  }

  res <- purrr::imap_dfr(scenario_data, get_model_terms) |>
    dplyr::filter(term != "(Intercept)") |>
    dplyr::group_by(term) |>
    dplyr::mutate(q_value = p.adjust(p.value, method = "holm")) |>
    dplyr::ungroup() |>
    dplyr::mutate(
      Question = dependent_var,
      PreSig = p.value <= 0.05,
      PostSig = q_value <= 0.05,
      Status = dplyr::case_when(
        PreSig & !PostSig ~ "Lost significance",
        !PreSig & PostSig ~ "Gained significance",
        PreSig & PostSig  ~ "Stayed significant",
        TRUE              ~ ""
      )
    ) |>
    dplyr::select(Question, Scenario, term, p.value, q_value, Status)
  
  res
}


lapply(LETTERS[1:10], run_Holm_logistics)

holm_results_letters <- purrr::map_dfr(LETTERS[1:10], run_Holm_logistics)
write.csv(holm_results_letters, "Holm_logistics_results_letters.csv", row.names = FALSE)



```
