---
title: "Comprehension Regressions: Follow-up Study"
output:
  html_document: default
  pdf_document: default
---

# Binomial Logistic Regressions — Follow-up Study Comprehension

We run binomial logistic regressions to test whether explanation type
(`EXPLN`), FAQ condition (`FAQ`), and domain experience predict correct
answers for each comprehension question (Q1–Q12).

Models are fit separately per scenario (Medical Simple, Medical Complex,
IoT Simple, IoT Complex). Benjamini-Hochberg (BH) correction is applied
across the four scenarios **within each predictor term**.

Results include odds ratios (OR), 95% confidence intervals, and
McFadden's R². They are saved to `BH_corrections_followup.csv`.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(broom)
library(purrr)
```

---

## Load data

```{r load-data}
scores_medicals <- read.csv('./data/followup/scores-meds.csv', encoding = 'UTF-8', header = TRUE)
scores_medicalc <- read.csv('./data/followup/scores-medc.csv', encoding = 'UTF-8', header = TRUE)
scores_iots     <- read.csv('./data/followup/scores-iots.csv', encoding = 'UTF-8', header = TRUE)
scores_iotc     <- read.csv('./data/followup/scores-iotc.csv', encoding = 'UTF-8', header = TRUE)

prepare_data <- function(df) {
  names(df) <- gsub(" ", "_", names(df))
  names(df)[names(df) == "Q12_x"] <- "Q12"
  df$EXPLN <- factor(df$EXPLN,
    levels = c("No explanation", "Unsubstantial", "Hardware", "Trust"))
  df$FAQ  <- factor(df$FAQ, levels = c("No FAQ", "Hide", "Show"))
  df$combined_CS_Experience      <- as.factor(df$combined_CS_Experience)
  df$combined_Medical_Experience <- as.factor(df$combined_Medical_Experience)
  df$combined_IoT_Experience     <- as.factor(df$combined_IoT_Experience)
  for (q in paste0("Q", 1:11)) {
    if (q %in% names(df)) df[[q]] <- factor(df[[q]], order = TRUE)
  }
  df
}

scores_medicals <- prepare_data(scores_medicals)
scores_medicalc <- prepare_data(scores_medicalc)
scores_iots     <- prepare_data(scores_iots)
scores_iotc     <- prepare_data(scores_iotc)
```

---


## Med Simple


```{r}
scores = scores_medicals

regression_model <- function(dependent_var) {
  formula_str <- as.formula(paste(dependent_var, "~ EXPLN + FAQ  + combined_Medical_Experience + combined_CS_Experience"))
  model <- glm(formula_str, data = scores, family = binomial)
  print(summary(model))
  print(Anova(model))
  plot_model(model)
  return(model)
}

```

```{r}
m = regression_model("Q1")

tidy(m) |>
  mutate(
    OR = exp(estimate),
    CI_low = exp(estimate - 1.96 * std.error),
    CI_high = exp(estimate + 1.96 * std.error)
  )

```

```{r}
regression_model("Q2")
```

```{r}
regression_model("Q3")
```

```{r}
regression_model("Q4")
```

```{r}
regression_model("Q5")
```

```{r}
regression_model("Q6")
```

```{r}
regression_model("Q7")
```

```{r}
regression_model("Q8")
```

```{r}
regression_model("Q9")
```

```{r}
regression_model("Q10")
```

```{r}
regression_model("Q11")
```

```{r}
regression_model("Q12")
```

## Med Complex


```{r}

scores = scores_medicalc

regression_model <- function(dependent_var) {
  formula_str <- as.formula(paste(dependent_var, "~ EXPLN + FAQ  + combined_Medical_Experience + combined_CS_Experience"))
  model <- glm(formula_str, data = scores, family = binomial)
  print(summary(model))
  print(Anova(model))
  plot_model(model)
  return(model)
}

```

```{r}
regression_model("Q1")
```

```{r}
regression_model("Q2")
```

```{r}
regression_model("Q3")
```

```{r}
regression_model("Q4")
```

```{r}
regression_model("Q5")
```

```{r}
regression_model("Q6")
```

```{r}
regression_model("Q7")
```

```{r}
regression_model("Q8")
```

```{r}
regression_model("Q9")
```

```{r}
regression_model("Q10")
```

```{r}
regression_model("Q11")
```

```{r}
regression_model("Q12")
```

## IoT Simple


```{r}

scores = scores_iots
regression_model <- function(dependent_var) {
  formula_str <- as.formula(paste(dependent_var, "~ EXPLN + FAQ  + combined_IoT_Experience + combined_CS_Experience"))
  model <- glm(formula_str, data = scores, family = binomial)
  print(summary(model))
  print(Anova(model))
  plot_model(model)
  return(model)
}

```

```{r}
regression_model("Q1")
```

```{r}
regression_model("Q2")
```

```{r}
regression_model("Q3")
```

```{r}
regression_model("Q4")
```

```{r}
regression_model("Q5")
```

```{r}
regression_model("Q6")
```

```{r}
regression_model("Q7")
```

```{r}
regression_model("Q8")
```

```{r}
regression_model("Q9")
```

```{r}
regression_model("Q10")
```

```{r}
regression_model("Q11")
```

```{r}
regression_model("Q12")
```

## IoT Complex


```{r}

scores = scores_iotc

regression_model <- function(dependent_var) {
  formula_str <- as.formula(paste(dependent_var, "~ EXPLN + FAQ  + combined_IoT_Experience + combined_CS_Experience"))
  model <- glm(formula_str, data = scores, family = binomial)
  print(summary(model))
  print(Anova(model))
  plot_model(model)
  return(model)
}

```

```{r}
regression_model("Q1")
```

```{r}
regression_model("Q2")
```

```{r}
regression_model("Q3")
```

```{r}
regression_model("Q4")
```

```{r}
regression_model("Q5")
```

```{r}
regression_model("Q6")
```

```{r}
regression_model("Q7")
```

```{r}
regression_model("Q8")
```

```{r}
regression_model("Q9")
```

```{r}
regression_model("Q10")
```

```{r}
regression_model("Q11")
```

```{r}
regression_model("Q12")
```

# Corrections
```{r}



run_BH_logistics <- function(dependent_var) {
  scenario_data <- list(
    MedicalSimple  = scores_medicals,
    MedicalComplex = scores_medicalc,
    IoTSimple      = scores_iots,
    IoTComplex     = scores_iotc
  )

  get_model_terms <- function(df, scenario) {
    exp_var <- if (grepl("Medical", scenario))
      "combined_Medical_Experience" else "combined_IoT_Experience"
    
    f <- as.formula(paste(
      dependent_var,
      "~ EXPLN + FAQ +",
      exp_var, "+ combined_CS_Experience"
    ))
    
    model <- glm(f, data = df, family = binomial)
    broom::tidy(model) |> dplyr::mutate(Scenario = scenario)
  }

  res <- purrr::imap_dfr(scenario_data, get_model_terms) |>
    dplyr::filter(term != "(Intercept)") |>
    dplyr::group_by(term) |>
    dplyr::mutate(q_value = p.adjust(p.value, method = "BH")) |>
    dplyr::ungroup() |>
    dplyr::mutate(
      Question = dependent_var,
      PreSig = p.value <= 0.05,
      PostSig = q_value <= 0.05,
      Status = dplyr::case_when(
        PreSig & !PostSig ~ "Lost significance",
        !PreSig & PostSig ~ "Gained significance",
        PreSig & PostSig  ~ "Stayed significant",
        TRUE              ~ ""
      )
    ) |>
    dplyr::select(Question, Scenario, term, p.value, q_value, Status)
    res
}
run_BH_logistics("Q1")
run_BH_logistics("Q2")
run_BH_logistics("Q3")
run_BH_logistics("Q4")
run_BH_logistics("Q5")
run_BH_logistics("Q6")
run_BH_logistics("Q7")
run_BH_logistics("Q8")
run_BH_logistics("Q9")
run_BH_logistics("Q10")
run_BH_logistics("Q11")
run_BH_logistics("Q12")

questions <- paste0("Q", 1:12)
holm_results <- purrr::map_dfr(questions, run_BH_logistics)
write.csv(holm_results, "BH_corrections_survey2.csv", row.names = FALSE)


```

```{r}
run_Holm_logistics <- function(dependent_var) {
  scenario_data <- list(
    MedicalSimple  = scores_medicals,
    MedicalComplex = scores_medicalc,
    IoTSimple      = scores_iots,
    IoTComplex     = scores_iotc
  )

  get_model_terms <- function(df, scenario) {

    exp_var <- if (grepl("Medical", scenario))
      "combined_Medical_Experience" else "combined_IoT_Experience"

    f <- as.formula(paste(
      dependent_var,
      "~ EXPLN + FAQ +",
      exp_var, "+ combined_CS_Experience"
    ))

    model <- glm(f, data = df, family = binomial)
      mcFadden <- 1 - (model$deviance / model$null.deviance)

    broom::tidy(model, conf.int = TRUE, conf.level = 0.95) |>
      dplyr::mutate(
        OR      = exp(estimate),
        OR_low  = exp(conf.low),
        OR_high = exp(conf.high),
        CI      = sprintf("[%.3f, %.3f]", OR_low, OR_high),
        Scenario = scenario,
        McFadden_R2 = mcFadden
      )
  }

  res <- purrr::imap_dfr(scenario_data, get_model_terms) |>
    dplyr::filter(term != "(Intercept)") |>
    dplyr::group_by(term) |>
    dplyr::mutate(q_value = p.adjust(p.value, method = "BH")) |>
    dplyr::ungroup() |>
    dplyr::mutate(
      Question = dependent_var,
      PreSig  = p.value <= 0.05,
      PostSig = q_value <= 0.05,
      Status  = dplyr::case_when(
        PreSig & !PostSig ~ "Lost significance",
        !PreSig & PostSig ~ "Gained significance",
        PreSig & PostSig  ~ "Stayed significant",
        TRUE              ~ ""
      )
    ) |>
    dplyr::select(
      Question, Scenario, term,
      estimate, OR, CI, OR_low, OR_high,
      p.value, q_value,McFadden_R2, Status
    )

  res
}

# Run all Q1–Q12

run_Holm_logistics("Q1")
run_Holm_logistics("Q2")
run_Holm_logistics("Q3")
run_Holm_logistics("Q4")
run_Holm_logistics("Q5")
run_Holm_logistics("Q6")
run_Holm_logistics("Q7")
run_Holm_logistics("Q8")
run_Holm_logistics("Q9")
run_Holm_logistics("Q10")
run_Holm_logistics("Q11")
run_Holm_logistics("Q12")


questions <- paste0("Q", 1:12)
holm_results <- purrr::map_dfr(questions, run_Holm_logistics)
write.csv(holm_results, "B-Holm_logistics_results_survey2.csv", row.names = FALSE)




```



```{r}
latex_or_ci_cell <- function(OR, lower, upper, digits = 2) {
  sprintf(
    "\\begin{tabular}{@{}c@{}} \n$%s$ \\\\[-2pt]\n{\\tiny [%s, %s]} \n\\end{tabular}",
    formatC(OR,    format = "f", digits = digits),
    formatC(lower, format = "f", digits = 3),
    formatC(upper, format = "f", digits = 3)
  )
}

holm_results <- holm_results |>
  dplyr::mutate(latex_cell = latex_or_ci_cell(OR, OR_low, OR_high))

```
