---
title: "Safety Aspects: With vs. Without TEE Information"
output:
  html_document: default
  pdf_document: default
---

# Do safety perceptions differ when participants have TEE information?

We test whether perceived safety across five aspects differs between
participants who received any TEE information (any explanation or FAQ)
and those who received none, separately per scenario.

A Mann-Whitney U test (`wilcox.test`, unpaired) is used for each
aspect × scenario combination. Benjamini-Hochberg (BH) correction is
applied across the five aspects **within each scenario**.

Results are saved to `Mann-Whitney_U_bh_corrections.csv`.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(purrr)
library(tibble)
```

---

## Load data

```{r load-data}
scores <- read.csv('./data/followup/scores_all_levels_safety.csv', header = TRUE)

safety_levels <- c(
  "Definitely safe", "Somewhat safe",
  "Neither safe nor unsafe",
  "Somewhat unsafe", "Definitely unsafe"
)

convert_to_numeric <- function(x) {
  factor(x, levels = safety_levels, labels = c(5, 4, 3, 2, 1))
}

scores <- scores |>
  dplyr::mutate(across(starts_with("safety_"), convert_to_numeric))

scores$EXPLN <- factor(scores$EXPLN,
  levels = c("No explanation", "Unsubstantial", "Hardware", "Trust"))
scores$FAQ   <- factor(scores$FAQ,
  levels = c("No FAQ", "Hide", "Show"))
scores$scenario <- factor(scores$scenario,
  levels = c("MedicalComplex", "MedicalSimple", "IoTComplex", "IoTSimple"))

# info = TRUE if participant received any explanation or FAQ
scores <- scores |>
  dplyr::mutate(info = !(EXPLN == "No explanation" & FAQ == "No FAQ"))
```

---

## Mann-Whitney U tests per scenario with BH correction

```{r run-tests}
scenarios <- c("MedicalComplex", "MedicalSimple", "IoTComplex", "IoTSimple")
aspects   <- c("safety_people", "safety_data", "safety_companyHospital",
               "safety_purpose", "safety_tee")

perform_test <- function(data, aspect) {
  numeric_data <- as.numeric(as.character(data[[aspect]]))
  test_data    <- data.frame(value = numeric_data, info = data$info)
  out          <- wilcox.test(value ~ info, data = test_data)
  tibble::tibble(
    aspect = aspect,
    W      = unname(out$statistic),
    p_raw  = out$p.value
  )
}

results <- purrr::map_dfr(scenarios, function(sc) {
  subset <- dplyr::filter(scores, .data$scenario == sc)
  purrr::map_dfr(aspects, ~perform_test(subset, .x)) |>
    dplyr::mutate(
      scenario = sc,
      p_BH    = p.adjust(p_raw, method = "BH"),
      PreSig  = p_raw <= 0.05,
      PostSig = p_BH  <= 0.05,
      Status  = dplyr::case_when(
        PreSig & !PostSig ~ "Lost significance",
        !PreSig & PostSig ~ "Gained significance",
        PreSig & PostSig  ~ "Stayed significant",
        TRUE              ~ "Not significant"
      )
    ) |>
    dplyr::select(scenario, aspect, W, p_raw, p_BH, Status)
})

write.csv(results, "Mann-Whitney_U_bh_corrections.csv", row.names = FALSE)
print(results)
```
