---
title: "regressions"
author: "Carolina Carreira"
date: ''
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ordinal)
library(lme4)
library(dplyr)
library(car)
library(sjPlot)
library(performance)
library(broom)
library(EMT)
library(multcomp)
library(emmeans)
library(RVAideMemoire)
library(ggplot2)
library(brant)
library(MASS)
library(pscl)

ENCODING = 'UTF-8'

```


Binomial logistic regression to check if demographic and experience
factors affect score (Medical Simple)

```{r}
regression_results <- read.csv('./data/firststudy/regression_willall-meds.csv', header = TRUE)
regression_results$gender <- as.factor(regression_results$gender)
regression_results$age <- as.factor(regression_results$age)
regression_results$combined_IoT_Experience <- as.factor(regression_results$combined_IoT_Experience)
regression_results$combined_Medical_Experience <- as.factor(regression_results$combined_Medical_Experience)
regression_results$combined_CS_Experience <- as.factor(regression_results$combined_CS_Experience)
names(regression_results) <- gsub(" ", "_", names(regression_results))  # Replace spaces with underscores
regression_results$EXPLN_S1 <- factor(regression_results$EXPLN_S1, levels = c("Unsubstantial", "Hardware", "Trust"))
regression_results$EXPLN_S2 <- as.factor(regression_results$EXPLN_S2)
regression_results$EXPLN_S3 <- as.factor(regression_results$EXPLN_S3)
regression_results$EXPLN_S3 <- as.factor(regression_results$EXPLN_S3)
regression_results$scenario_complexity <- as.factor(regression_results$scenario_complexity)
regression_results$scenario_scenario <- as.factor(regression_results$scenario_scenario)
regression_results$scenario <- factor(regression_results$scenario, levels = c("MedicalComplex", "MedicalSimple", "IoTComplex", "IoTSimple"))


regression_results$safety_pre <- as.factor(ordered(regression_results$safety_pre,
                                       levels = c("Not at all safe", "Somewhat safe","Completely safe")))
regression_results$safety_post <- as.factor(ordered(regression_results$safety_post,
                                       levels = c("Not at all safe", "Somewhat safe","Completely safe")))
regression_results$willingness <- as.factor(ordered(regression_results$willingness,
                                       levels = c("Would not", "Maybe would","Definitely would")))


scores_medicals = regression_results

```

```{r}

regression_model <- function(dependent_var) {
  formula_str <- as.formula(paste(dependent_var, "~ EXPLN_S1 + EXPLN_S2 + EXPLN_S3 + combined_Medical_Experience + combined_CS_Experience"))
  
  model_output <- clm(formula_str, data = regression_results, Hess=TRUE, nAGQ = 10)
  print(model_output)
  print(summary(model_output))
  return(model_output)
}

test_proportional_odds <- function(dependent_var) {
  data <- regression_results
  formula_str <- as.formula(paste(dependent_var, "~ EXPLN_S1 + EXPLN_S2 + EXPLN_S3 + combined_Medical_Experience + combined_CS_Experience"))
  model_clm <- clm(formula_str, data = data, Hess = TRUE, nAGQ = 10)
  polr_model <- polr(formula_str, data = data, Hess = TRUE)
  brant_result <- brant(polr_model)
  print(brant_result)
  p_values <- brant_result[, "probability"]
  cat("\nBrant Test Results:\n")
  print(brant_result)
  if (any(p_values < 0.05, na.rm = TRUE)) {
    cat("\nThe Proportional Odds Assumption does NOT hold for at least one predictor.\n")
    cat("Consider using a partial proportional odds model or another approach.\n")
  } else {
    cat("\nThe Proportional Odds Assumption holds for all predictors.\n")
  }
}

```

## Medical simple

```{r}
regression_model("safety_pre")
test_proportional_odds("safety_pre")

```

```{r}
regression_model("safety_post")
test_proportional_odds("safety_post")
```

```{r}
regression_model("willingness")
test_proportional_odds("willingness")
```

Binomial logistic regression to check if demographic and experience
factors affect score (Medical Complex)

```{r}
regression_results <- read.csv('./data/firststudy/regression_willall-medc.csv', header = TRUE)
regression_results$gender <- as.factor(regression_results$gender)
regression_results$age <- as.factor(regression_results$age)
regression_results$combined_IoT_Experience <- as.factor(regression_results$combined_IoT_Experience)
regression_results$combined_Medical_Experience <- as.factor(regression_results$combined_Medical_Experience)
regression_results$combined_CS_Experience <- as.factor(regression_results$combined_CS_Experience)
names(regression_results) <- gsub(" ", "_", names(regression_results))  # Replace spaces with underscores
regression_results$EXPLN_S1 <- factor(regression_results$EXPLN_S1, levels = c("Unsubstantial", "Hardware", "Trust"))
regression_results$EXPLN_S2 <- as.factor(regression_results$EXPLN_S2)
regression_results$EXPLN_S3 <- as.factor(regression_results$EXPLN_S3)
regression_results$EXPLN_S3 <- as.factor(regression_results$EXPLN_S3)
regression_results$scenario_complexity <- as.factor(regression_results$scenario_complexity)
regression_results$scenario_scenario <- as.factor(regression_results$scenario_scenario)
regression_results$scenario <- factor(regression_results$scenario, levels = c("MedicalComplex", "MedicalSimple", "IoTComplex", "IoTSimple"))


regression_results$safety_pre <- as.factor(ordered(regression_results$safety_pre,
                                       levels = c("Not at all safe", "Somewhat safe","Completely safe")))
regression_results$safety_post <- as.factor(ordered(regression_results$safety_post,
                                       levels = c("Not at all safe", "Somewhat safe","Completely safe")))
regression_results$willingness <- as.factor(ordered(regression_results$willingness,
                                       levels = c("Would not", "Maybe would","Definitely would")))

scores_medicalc = regression_results
    
```

```{r}

regression_model <- function(dependent_var) {
  formula_str <- as.formula(paste(dependent_var, "~ EXPLN_S1 + EXPLN_S2 + EXPLN_S3 + combined_Medical_Experience + combined_CS_Experience"))
  
  model_output <- clm(formula_str, data = regression_results, Hess=TRUE, nAGQ = 10)
  print(model_output)
  print(summary(model_output))
  return()
}

test_proportional_odds <- function(dependent_var) {
  data <- regression_results
  formula_str <- as.formula(paste(dependent_var, "~ EXPLN_S1 + EXPLN_S2 + EXPLN_S3 + combined_Medical_Experience + combined_CS_Experience"))
  model_clm <- clm(formula_str, data = data, Hess = TRUE, nAGQ = 10)
  polr_model <- polr(formula_str, data = data, Hess = TRUE)
  brant_result <- brant(polr_model)
  print(brant_result)
  p_values <- brant_result[, "probability"]
  cat("\nBrant Test Results:\n")
  print(brant_result)
  if (any(p_values < 0.05, na.rm = TRUE)) {
    cat("\nThe Proportional Odds Assumption does NOT hold for at least one predictor.\n")
    cat("Consider using a partial proportional odds model or another approach.\n")
  } else {
    cat("\nThe Proportional Odds Assumption holds for all predictors.\n")
  }
}

```

## Medical complex

```{r}
regression_model("safety_pre")
test_proportional_odds("safety_pre")
```
```{r}
regression_model("safety_post")
test_proportional_odds("safety_post")
```

```{r}
regression_model("willingness")
test_proportional_odds("willingness")
```

Binomial logistic regression to check if demographic and experience
factors affect score (IoT Simple)

```{r}
regression_results <- read.csv('./data/firststudy/regression_willall-iots.csv', header = TRUE)
regression_results$gender <- as.factor(regression_results$gender)
regression_results$age <- as.factor(regression_results$age)
regression_results$combined_IoT_Experience <- as.factor(regression_results$combined_IoT_Experience)
regression_results$combined_Medical_Experience <- as.factor(regression_results$combined_Medical_Experience)
regression_results$combined_CS_Experience <- as.factor(regression_results$combined_CS_Experience)
names(regression_results) <- gsub(" ", "_", names(regression_results))  # Replace spaces with underscores
regression_results$EXPLN_S1 <- factor(regression_results$EXPLN_S1, levels = c("Unsubstantial", "Hardware", "Trust"))
regression_results$EXPLN_S2 <- as.factor(regression_results$EXPLN_S2)
regression_results$EXPLN_S3 <- as.factor(regression_results$EXPLN_S3)
regression_results$EXPLN_S3 <- as.factor(regression_results$EXPLN_S3)
regression_results$scenario_complexity <- as.factor(regression_results$scenario_complexity)
regression_results$scenario_scenario <- as.factor(regression_results$scenario_scenario)
regression_results$scenario <- factor(regression_results$scenario, levels = c("MedicalComplex", "MedicalSimple", "IoTComplex", "IoTSimple"))


regression_results$safety_pre <- as.factor(ordered(regression_results$safety_pre,
                                       levels = c("Not at all safe", "Somewhat safe","Completely safe")))
regression_results$safety_post <- as.factor(ordered(regression_results$safety_post,
                                       levels = c("Not at all safe", "Somewhat safe","Completely safe")))
regression_results$willingness <- as.factor(ordered(regression_results$willingness,
                                       levels = c("Would not", "Maybe would","Definitely would")))

scores_iots = regression_results
    
```

```{r}

regression_model <- function(dependent_var) {
  formula_str <- as.formula(paste(dependent_var, "~ EXPLN_S1 + EXPLN_S2 + EXPLN_S3 + combined_IoT_Experience + combined_CS_Experience"))
  
  model_output <- clm(formula_str, data = regression_results, Hess=TRUE, nAGQ = 10)
  print(model_output)
  print(summary(model_output))
  return()
}

test_proportional_odds <- function(dependent_var) {
  data <- regression_results
  formula_str <- as.formula(paste(dependent_var, "~ EXPLN_S1 + EXPLN_S2 + EXPLN_S3 + combined_IoT_Experience + combined_CS_Experience"))
  model_clm <- clm(formula_str, data = data, Hess = TRUE, nAGQ = 10)
  polr_model <- polr(formula_str, data = data, Hess = TRUE)
  brant_result <- brant(polr_model)
  print(brant_result)
  p_values <- brant_result[, "probability"]
  cat("\nBrant Test Results:\n")
  print(brant_result)
  if (any(p_values < 0.05, na.rm = TRUE)) {
    cat("\nThe Proportional Odds Assumption does NOT hold for at least one predictor.\n")
    cat("Consider using a partial proportional odds model or another approach.\n")
  } else {
    cat("\nThe Proportional Odds Assumption holds for all predictors.\n")
  }
}

```

## IoT simple

```{r}
regression_model("safety_pre")
test_proportional_odds("safety_pre")
```
```{r}
regression_model("safety_post")
test_proportional_odds("safety_post")
```

```{r}
regression_model("willingness")
test_proportional_odds("willingness")
```

Binomial logistic regression to check if demographic and experience
factors affect score (IoT Complex)

```{r}
regression_results <- read.csv('./data/firststudy/regression_willall-iotc.csv', header = TRUE)
regression_results$gender <- as.factor(regression_results$gender)
regression_results$age <- as.factor(regression_results$age)
regression_results$combined_IoT_Experience <- as.factor(regression_results$combined_IoT_Experience)
regression_results$combined_Medical_Experience <- as.factor(regression_results$combined_Medical_Experience)
regression_results$combined_CS_Experience <- as.factor(regression_results$combined_CS_Experience)
names(regression_results) <- gsub(" ", "_", names(regression_results))  # Replace spaces with underscores
regression_results$EXPLN_S1 <- factor(regression_results$EXPLN_S1, levels = c("Unsubstantial", "Hardware", "Trust"))
regression_results$EXPLN_S2 <- as.factor(regression_results$EXPLN_S2)
regression_results$EXPLN_S3 <- as.factor(regression_results$EXPLN_S3)
regression_results$EXPLN_S3 <- as.factor(regression_results$EXPLN_S3)
regression_results$scenario_complexity <- as.factor(regression_results$scenario_complexity)
regression_results$scenario_scenario <- as.factor(regression_results$scenario_scenario)
regression_results$scenario <- factor(regression_results$scenario, levels = c("MedicalComplex", "MedicalSimple", "IoTComplex", "IoTSimple"))


regression_results$safety_pre <- as.factor(ordered(regression_results$safety_pre,
                                       levels = c("Not at all safe", "Somewhat safe","Completely safe")))
regression_results$safety_post <- as.factor(ordered(regression_results$safety_post,
                                       levels = c("Not at all safe", "Somewhat safe","Completely safe")))
regression_results$willingness <- as.factor(ordered(regression_results$willingness,
                                       levels = c("Would not", "Maybe would","Definitely would")))

scores_iotc = regression_results
```

```{r}

regression_model <- function(dependent_var) {
  formula_str <- as.formula(paste(dependent_var, "~ EXPLN_S1 + EXPLN_S2 + EXPLN_S3 + combined_IoT_Experience + combined_CS_Experience"))
  
  model_output <- clm(formula_str, data = regression_results, Hess=TRUE, nAGQ = 10)
  print(model_output)
  print(summary(model_output))
  return()
}

test_proportional_odds <- function(dependent_var) {
  data <- regression_results
  formula_str <- as.formula(paste(dependent_var, "~ EXPLN_S1 + EXPLN_S2 + EXPLN_S3 + combined_IoT_Experience + combined_CS_Experience"))
  model_clm <- clm(formula_str, data = data, Hess = TRUE, nAGQ = 10)
  polr_model <- polr(formula_str, data = data, Hess = TRUE)
  brant_result <- brant(polr_model)
  print(brant_result)
  p_values <- brant_result[, "probability"]
  cat("\nBrant Test Results:\n")
  print(brant_result)
  if (any(p_values < 0.05, na.rm = TRUE)) {
    cat("\nThe Proportional Odds Assumption does NOT hold for at least one predictor.\n")
    cat("Consider using a partial proportional odds model or another approach.\n")
  } else {
    cat("\nThe Proportional Odds Assumption holds for all predictors.\n")
  }
}

```

## IoT complex

```{r}
regression_model("safety_pre")
test_proportional_odds("safety_pre")
```
```{r}
regression_model("safety_post")
test_proportional_odds("safety_post")
```

```{r}
regression_model("willingness")
test_proportional_odds("willingness")
```

# Corrections

```{r}





run_BH <- function(dependent_var) {
  scenario_data <- list(
    MedicalSimple  = scores_medicals,
    MedicalComplex = scores_medicalc,
    IoTSimple      = scores_iots,
    IoTComplex     = scores_iotc
  )

  compute_r2 <- function(full_model, data, dependent_var) {
    null_formula <- as.formula(paste(dependent_var, "~ 1"))
    null_model <- clm(null_formula, data = data, Hess = TRUE, nAGQ = 1)

    ll_full <- as.numeric(logLik(full_model))
    ll_null <- as.numeric(logLik(null_model))
    n <- nobs(full_model)

    r2 <- (1 - exp((2/n) * (ll_null - ll_full))) / (1 - exp(2*ll_null/n))
    return(r2)
  }

  get_model_terms <- function(df, scenario) {

    exp_var <- if (grepl("Medical", scenario))
      "combined_Medical_Experience" else "combined_IoT_Experience"

    f <- as.formula(paste(
      dependent_var,
      "~ EXPLN_S1 + EXPLN_S2 + EXPLN_S3 +",
      exp_var, "+ combined_CS_Experience"
    ))

    model <- clm(f, data = df, Hess = TRUE, nAGQ = 10)

    # compute Nagelkerke R2 correctly
    R2_Nagelkerke <- compute_r2(model, df, dependent_var)

    broom::tidy(model, conf.int = TRUE, conf.level = 0.95) |>
      mutate(
        OR      = exp(estimate),
        OR_low  = exp(conf.low),
        OR_high = exp(conf.high),
        CI      = sprintf("[%.3f, %.3f]", OR_low, OR_high),
        Scenario = scenario,
        R2_Nagelkerke = R2_Nagelkerke
      )
  }

  purrr::imap_dfr(scenario_data, get_model_terms) |>
    filter(term != "(Intercept)") |>
    group_by(term) |>
    mutate(q_value = p.adjust(p.value, method = "BH")) |>
    ungroup() |>
    mutate(
      Question = dependent_var,
      PreSig  = p.value <= 0.05,
      PostSig = q_value <= 0.05,
      Status = case_when(
        PreSig & !PostSig ~ "Lost significance",
        !PreSig & PostSig ~ "Gained significance",
        PreSig & PostSig  ~ "Stayed significant",
        TRUE ~ ""
      )
    ) |>
    dplyr::select(
      Question, Scenario, term,
      estimate, OR, CI, OR_low, OR_high,
      p.value, q_value, Status,
      R2_Nagelkerke
    )
}



write.csv(run_BH("willingness"), "BH_correction_1stStudy_will.csv", row.names = FALSE)


write.csv(run_BH("safety_pre"), "BH_correction_1stStudy_safety.csv", row.names = FALSE)

```


